\documentclass{article}

\usepackage{mathtools,amsfonts,amsthm,amssymb} 
\usepackage{multicol}
\usepackage[margin=2.7cm]{geometry}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{url}
\usepackage{etaremune}
\hypersetup{
	colorlinks,
	linkcolor={black},
	citecolor={blue!50!black},
	urlcolor={red!40!black}
}

\title{CV}
\author{Toghrul Karimov}
\date{Max Planck Institute for Software Systems, Saarbr\"ucken, Germany}
\date{}

\begin{document}
	\begin{center}
		\bfseries\huge Toghrul Karimov
	\end{center}
	\begin{center}
		\large
		\{email: toghs@mpi-sws.org, website: toghrul-karimov.github.io\}
	\end{center}
	\section*{Academic employment\footnote{I am currently employed by the Max Planck Institute for Software Systems in Saarbrücken, Germany, and paid by an ERC Synergy grant between Paris and Saarbrücken. I travel regularly to Paris, where I work with V. Berth\'e and others.}}
	\begin{minipage}{0.3\textwidth}
		\hspace{0.1cm} \textbf{04/2025 - present}
	\end{minipage}
	\vspace*{0.25cm}
	\begin{minipage}{0.7\textwidth}
		Postdoctoral researcher working with Val\'erie Berth\'e (Institut de Recherche en Informatique Fondamental, Paris, France)  
		%and Jo\"el Ouaknine (Max Planck Institute for Software Systems, Saarbr\"ucken)
		
		\vspace*{0.2cm}
		
		Funded by the ERC Synergy Grant ``DnyAMiCs''
		\vspace{0.3cm}
	\end{minipage}
	\vspace{0.85cm}
	\begin{minipage}{0.3\textwidth}
		\hspace{0.1cm} \textbf{03/2024 - 03/2025}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		Postdoctoral researcher working with Jo\"el Ouaknine (Max Planck Institute for Software Systems, Saarbr\"ucken, Germany)
	\end{minipage}
	
	
	\section*{Education}
	\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{2019-2024}
	\end{minipage}
	\vspace*{0.25cm}
	\begin{minipage}{0.7\textwidth}
		PhD student at Saarland University and the Max Planck Institute for Software Systems, Saarbrücken, Germany
		
		\vspace*{0.2cm}
		Supervisor: Jo\"el Ouaknine 
		
		\vspace*{0.2cm}
		Thesis: Algorithmic verification of linear dynamical systems \href{https://doi.org/doi:10.22028/D291-41630}{doi}
		
		\vspace*{0.2cm}
		Co-received the Ackermann Award 2025
		% nominated for various dissertation awards (outcomes pending)
		\vspace{0.3cm}
	\end{minipage}
	\vspace{0.85cm}
	\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{2015-2019}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		MCompSci Computer Science, University of Oxford, UK
		
		\vspace*{0.2cm}
		First Class Honours
	\end{minipage}
	%\section*{Research areas}
	%\begin{itemize}
	%	\item I am a theoretical computer scientist working on decision problems that lie at the intersection of dynamical systems, number theory, logic, and automata theory.
	%	\item My PhD thesis was about decision problems that arise in verification of linear dynamical systems.
	%\end{itemize}
	
	\section*{Scholarships and awards}
	\begin{etaremune}
		\item EACSL \textbf{Outstanding Dissertation Award} for Logic in Computer Science (Ackermann Award) 2025.
		
		\item \textbf{Fellowship} of the Hausdorff Research Institute for Mathematics (HIM) in Bonn to attend the Trimester Program ``Definability, Decidability, and Computability'', October 2025 
		
		\item ACM-SIGBED \textbf{Best Paper Award} at the conference Hybrid Systems: Computation and Control (HSCC) 2024 for the paper ``Linear dynamical systems with continuous weight functions'' together with R. Aghamov, C. Baier, J. Ouaknine, and J. Piribauer. 
		\item \textbf{Distinguished Paper Award} at the conference ACM/IEEE Symposium on Logic in Computer Science (LICS) 2024 for the paper ``On the decidability of monadic second-order logic with arithmetic predicates'' together with V. Berth\'e, J. Nieuvweld, J. Ouaknine, M. Vahanwala, and J. Worrell. 
		\item CPEC (see \url{www.perspicuous-computing.science}) \textbf{mini-project award} for a two-week research visit to University of Oxford, June 2022.
		\item Keble College \textbf{Scholarship}, 2016-2019. Awarded for excellent academic performance at the end of each year.
		\item The \textbf{Scholarship} of the Ministry of Education of Azerbaijan covering the full costs of my study at the University of Oxford, 2015-2019.
	\end{etaremune}
	
	\vspace*{0.2cm}
	\section*{Teaching}
	
	\noindent\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{Winter 2022}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		``Topics in algorithmic dynamical systems theory'', teaching assistant 
		
		Saarland University
	\end{minipage}
	
	\vspace{0.3cm}
	
	\noindent\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{Summer 2020}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		``Automata and sequences'', teaching assistant 
		
		Saarland University
	\end{minipage}
	
	\vspace*{0.4cm}
	\section*{Invited talks and presentations}
	\begin{etaremune}
		\item
		Decidability of logical theories via rigidity and randomness in dynamical systems.
		% (conference presentation). 
		\emph{Algebraic Methods in Dynamics and Particle Physics}, Saarbr\"ucken, Germany, 2025. \href{https://dynaverse2025.mpi-sws.org/decidability-of-logical-theories-via-rigidity-and-randomness-in-dynamical-systems/}{abstract and slides}
		
		\item Some applications of o-minimality to computational problems in dynamical systems theory (seminar talk). \emph{Hausdorff Research Institute for Mathematics}, Bonn, Germany, 2025. 
		\href{https://www.youtube.com/watch?v=xwqYA9wns4g}{video recording}
		
		\item Arithmetic predicates and decidability of logical theories (invited talk).
		\emph{Hausdorff Research Institute for Mathematics}, Bonn, Germany, 2025.
		\href{https://www.youtube.com/watch?v=SYknkHCvM68}{video recording}
		
		\item Extensions of linear programming with squares and powers of integers (invited talk). \emph{Kyoto University}, Japan, 2025.
		
		\item Rich sequences and decidability of logical theories.
		% (conference presentation). 
		\emph{Numeration and Substitution 2025}, Tsukuba, Japan. \href{https://numeration2025.sciencesconf.org/}{conference website}
		
		\item Ergodicity for linear dynamical systems via o-minimality. %(conference presentation). 
		\emph{Highlights of Logic, Games, and Automata 2025}, Saarbr\"ucken, Germany. \href{https://highlights-conference.org/2025/}{conference website}
		
		\item From word combinatorics to automatic structures (invited talk), \emph{Workshop on Recent Developments in Arithmetic Theories and Applications}, Kolkata, India, 2025. \href{https://logicindia.org/icla/icla2025/}{conference website}
		
		\item On the decidability of Presburger arithmetic expanded with powers (paper presentation). \emph{Symposium on Discrete Algorithm (SODA) 2025}, New Orleans, United States. \href{https://meetings.siam.org/sess/dsp_talk.cfm?p=145077}{abstract}
		
		\item Ode to o-minimality (invited talk). \emph{Symbolic Dynamics and Arithmetic Expansions}, Roscoff, France, and \emph{Stellenbosch University Logic Seminar}, South Africa, 2024. \href{https://www.irif.fr/~symdynar/uploads/Main/karimov_roscoff.pdf}{slides}
		
		\item The power of Positivity (paper presentation). \emph{Logic in Computer Science (LICS) 2023}, Boston, United States. \href{https://lics.siglog.org/archive/2023/}{conference website}
		
		\item The model-checking problem for linear dynamical systems. \emph{Workshop on Algorithmic Aspects of Dynamical Systems}, Barbados, 2023. \href{https://bellairs2023.mpi-sws.org/}{conference website}
		
		\item The pseudo-reachability problem for diagonalisable affine dynamical systems (paper presentation). \emph{Mathematical Foundations of Computer Science (MFCS) 2022}, Vienna, Austria, and \emph{Reachability Problems (RP) 2022}, Saarbr\"ucken, Germany. \href{https://www.ac.tuwien.ac.at/mfcs2022/accepted/}{conference website}, 
		\href{https://rp2022.mpi-sws.org/program.html}{conference website}
		
		\item The pseudo-Skolem problem is decidable (paper presentation). \emph{Mathematical Foundations of Computer Science (MFCS) 2021}, Tallinn, Estonia. \href{https://compose.ioc.ee/mfcs/accepted.php}{conference website}
		
		\item Invariants and impossibility: from geometric constructions to solving polynomial equations. \emph{Monsoon Math 2021}, an online camp for Indian students.
		
		\item Deciding $\omega$-regular properties on linear recurrence sequences (paper presentation). \emph{Principles of Programming Languages (POPL) 2021}, online. \href{https://popl21.sigplan.org/profile/toghrulkarimov}{abstract}
		
		\item  On LTL model-checking for low-dimensional discrete
		linear dynamical systems. \emph{Mathematical Foundations of Computer Science (MFCS) 2020}, online. \href{http://mfcs.mff.cuni.cz/2020/}{conference website}
	\end{etaremune}
	
	\vspace*{0.15cm}
	\section*{Publications in reverse chronological order\footnote{In theoretical computer science, the authors of a paper are usually listed in the alphabetical order. The papers in which Toghrul Karimov was the clear lead author are marked with an asterisk.}}
	
	\begin{etaremune}
		\item 
		{\large *Linear dynamical systems with weight functions} 
		\href{https://toghrul-karimov.github.io/assets/papers/nahs-weights.pdf}{pdf}
		\vspace*{0.2cm}\newline
		R. Aghamov, C. Baier, T. Karimov, J. Piribauer, and J. Ouaknine
		\vspace*{0.25cm}\newline
		\emph{Nonlinear Analysis: Hybrid Systems, Vol.\ 60}
		\vspace*{0.2cm}
		
		\item
		{\large Model checking linear temporal logic with standpoint modalities}
		\href{https://doi.org/10.24963/kr.2025/}{doi}
		\vspace*{0.2cm}\newline
		R. Aghamov, C. Baier, T. Karimov, R. Majumdar, J. Ouaknine, J. Piribauer, and T. Spork%
		\vspace*{0.25cm}\newline 
		\emph{Principles of Knowledge Representation and Reasoning (KR) 2025}
		\vspace{0.2cm}
		
		\item
		{\large Multiple reachability in linear dynamical systems}
		\href{https://doi.org/10.1109/LICS65433.2025.00055}{doi}
		\vspace*{0.2cm}\newline
		T. Karimov, E. Kelmendi, J. Ouaknine, and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Logic in Computer Science (LICS) 2025}
		\vspace{0.2cm}
		
		\item
		{\large Algorithmic applications of Schanuel's conjecture}
		\href{https://doi.org/10.1007/978-3-031-97439-7_5}{doi}
		\vspace*{0.2cm}\newline
		T. Karimov, J. Nieuwveld, J. Ouaknine, M. Vahanwala and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Principles of Formal Quantitative Analysis: Essays Dedicated to Christel Baier on the Occasion of Her 60th Birthday}
		\vspace{0.2cm}
		
		\item
		{\large *Verification of linear dynamical systems via o-minimality of the real numbers}
		\href{https://doi.org/10.4230/LIPIcs.ICALP.2025.163}{doi}%
		\vspace*{0.2cm}\newline
		T. Karimov
		\vspace*{0.25cm}\newline
		\emph{International Colloquium on Automata, Languages, and Programming (ICALP) 2025}
		\vspace{0.2cm}
		
		\item 
		{\large On the decidability of Presburger arithmetic expanded with powers} \href{https://doi.org/10.1137/1.9781611978322.89}{doi}
		\vspace*{0.2cm}\newline
		T. Karimov, F. Luca, J. Nieuwveld, J. Ouaknine, and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Symposium on Discrete Algorithms (SODA) 2025}
		\vspace{0.2cm}
		
		\item
		{\large *The monadic theory of toric words} \href{https://doi.org/10.1016/j.tcs.2024.114959}{doi}
		\vspace*{0.2cm}\newline
		V. Berth\'e, T. Karimov, J. Nieuwveld, J. Ouaknine, M. Vahanwala, and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Theoretical Computer Science, Vol.\ 1025}
		\vspace*{0.2cm}
		
		\item{\large On the decidability of monadic second-order logic with arithmetic predicates}  \href{https://doi.org/10.1145/3661814.3662119}{doi}
		\vspace*{0.2cm}
		\newline
		V. Berth\'e, T. Karimov, J. Nieuwveld, J. Ouaknine, M. Vahanwala, and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Logic in Computer Science (LICS) 2024} 
		
		\textbf{Distinguished Paper Award} 
		\vspace*{0.2cm}
		
		\item 
		{\large *Linear dynamical systems with continuous weight functions}
		\href{https://doi.org/10.1145/3641513.3650173}{doi}
		\vspace*{0.2cm}
		\newline
		R. Aghamov, C. Baier, T. Karimov, J. Piribauer, and J. Ouaknine
		\vspace*{0.25cm}\newline
		\emph{Hybrid Systems: Computation and Control (HSCC) 2024} 
		
		\textbf{ACM SIGBED Best Paper Award}
		\vspace*{0.2cm}
		
		\item 
		{\large Model checking Markov chains as distribution transformers}
		\href{https://doi.org/10.1007/978-3-031-75775-4_13}{doi}
		\vspace{0.2cm}\newline
		R. Aghamov, C. Baier, T. Karimov, J. Nieuwveld, J. Ouaknine and M. Vahanwala
		\vspace*{0.25cm}\newline
		\emph{Principles of Verification: Cycling the Probabilistic Landscape. Essays Dedicated to Joost-Pieter Katoen on the Occasion of His 60th Birthday, Part II}
		\vspace*{0.2cm}
		
		\item 
		{\large *The power of Positivity}
		\href{https://doi.org/10.1109/LICS56636.2023.10175758}{doi}
		\vspace{0.2cm}\newline
		T. Karimov, E. Kelmendi, J. Nieuwveld, J. Ouaknine and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{ACM/IEEE Symposium on Logic in Computer Science (LICS) 2023} 
		\vspace*{0.2cm}
		
		\item 
		{\large *What's decidable about discrete linear dynamical systems?}
		\href{https://doi.org/10.1007/978-3-031-22337-2_2}{doi}
		\vspace{0.2cm}\newline
		T. Karimov, E. Kelmendi, J. Ouaknine and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{Principles of Systems Design: Essays Dedicated to Thomas A. Henzinger on the Occasion of His 60th Birthday}
		\vspace*{0.2cm}
		
		\item 
		{\large Parameter synthesis for parametric probabilistic dynamical systems and \\[0.2cm] prefix-independent specifications}
		\href{https://doi.org/10.4230/LIPIcs.CONCUR.2022.10}{doi}
		\vspace{0.2cm}\newline
		C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, J. Ouaknine, D. Purser, M.~Whiteland, and J. Worrell
		\vspace*{0.25cm}\newline\emph{International Conference on Concurrency Theory (CONCUR) 2022}
		\vspace*{0.2cm}
		
		\item 
		{\large *The pseudo-reachability problem for diagonalisable linear dynamical systems}
		\href{https://doi.org/10.4230/LIPIcs.MFCS.2022.40}{doi}
		\vspace{0.2cm}\newline
		J. D'Costa, T. Karimov, R. Majumdar, J. Ouaknine, M. Salamati, and J. Worrell
		\vspace*{0.25cm}\newline\emph{Mathematical Foundations of Computer Science (MFCS) 2022}%
		\vspace*{0.2cm}
		
		\item 
		{\large *What's decidable about linear loops?}
		\href{https://doi.org/10.1145/3498727}{doi}
		\vspace{0.2cm}\newline
		T. Karimov, E. Lefaucheux, J. Ouaknine, D. Purser, J. Worrell, and M. Whiteland
		\vspace*{0.25cm}\newline
		\emph{POPL 2022, Proceedings of the ACM on Programming Languages, Vol. 6}
		\vspace*{0.2cm}
		
		\item 
		{\large The orbit problem for parametric linear dynamical systems}
		\href{https://doi.org/10.4230/LIPIcs.CONCUR.2021.28}{doi}
		\vspace{0.2cm}\newline
		C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, F. Luca, J. Ouaknine, D. Purser, M.~Whiteland, and J. Worrell
		\vspace*{0.25cm}\newline \emph{International Conference on Concurrency Theory (CONCUR) 2021}
		\vspace*{0.2cm}
		
		\item 
		{\large *The pseudo-Skolem problem is decidable}
		\href{https://doi.org/10.4230/LIPIcs.MFCS.2021.34}{doi}
		\vspace{0.2cm}\newline
		J. D'Costa, T. Karimov, R. Majumdar, J. Ouaknine, M. Salamati, S. Soudjani, and J. Worrell%
		\vspace*{0.25cm}\newline 
		\emph{Mathematical Foundations of Computer Science (MFCS) 2021}%
		\vspace*{0.2cm}
		
		\item 
		{\large *Deciding $\omega$-regular properties on linear recurrence sequences}
		\href{https://doi.org/10.1145/3434329}{doi}
		\vspace{0.2cm}\newline
		S. Almagor, T. Karimov, E. Kelmendi, J. Ouaknine, and J. Worrell
		\vspace*{0.25cm}\newline
		\emph{POPL 2021, Proceedings of the ACM on Programming Languages, Vol. 5}
		\vspace*{0.2cm} 
		
		\item
		{\large Reachability in dynamical systems with rounding} 
		\href{https://doi.org/10.4230/LIPIcs.FSTTCS.2020.36}{doi}
		\vspace{0.2cm} \newline
		C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, J. Ouaknine,
		A. Pouly, D. Purser, and M. Whiteland
		\vspace*{0.25cm}\newline                 
		\emph{Foundations of Software Technology and Theoretical Computer Science (FSTTCS) 2020}
		\vspace*{0.2cm}
		
		\item 
		\large {*On LTL model-checking for low-dimensional discrete linear dynamical systems}
		\href{https://doi.org/10.4230/LIPIcs.MFCS.2020.54}{doi}
		\vspace{0.25cm}\newline       
		T. Karimov, J. Ouaknine, and J. Worrell
		\vspace*{0.2cm}\newline 
		\emph{Mathematical Foundations of Computer Science (MFCS) 2020}
		\vspace*{0.2cm}
	\end{etaremune}
	
	\vspace*{0.1cm}
	
	\section*{Papers under peer review}
	\begin{itemize}
		\item
		{\large Automata on $S$-adic words}
		\href{https://arxiv.org/abs/2506.17460}{arXiv}
		\vspace{0.2cm} \newline
		V. Berth\'e, T. Karimov, and M. Vahanwala
		\vspace*{0.2cm}
		
		\item 
		{\large Preservation theorems for transducers outputs}
		\href{https://toghrul-karimov.github.io/assets/papers/preservation-theorems.pdf}{pdf}
		\vspace{0.2cm} \newline
		V. Berth\'e, H. Goulet-Oullet, T. Karimov, D.Perrin, and M. Vahanwala
		\vspace*{0.2cm}
		
		\item 
		{\large *Rich sequences and decidability of logical theories}
		\href{https://toghrul-karimov.github.io/assets/papers/rich-sequences.pdf}{pdf}
		\vspace{0.2cm} \newline
		T. Karimov, J, Nieuwveld, and J. Ouaknine
		\vspace*{0.2cm}
		
		\item
		{\large On the decidability of monadic theories of arithmetic predicates
		}
		\href{https://arxiv.org/abs/2405.07953}{arXiv}
		\vspace{0.2cm} \newline
		V. Berth\'e, T. Karimov, J. Nieuwveld, J. Ouaknine, M. Vahanwala, and J. Worrell
		\vspace*{0.2cm}
	\end{itemize}
\end{document}