\documentclass{article}
\usepackage[margin=3cm]{geometry}
\usepackage[hidelinks]{hyperref}
\title{\bfseries\Huge Toghrul Karimov}
\author{\{email: toghs@mpi-sws.org, website: toghrul-karimov.github.io\}}
\date{}
\begin{document}
	\maketitle
	
	Postdoctoral researcher at the Max Planck Institute for Software Systems in Saarbr\"ucken, Germany since February 2024.
	
	\section*{Education}
		\begin{minipage}{0.3\textwidth}
			\hspace{0.5cm} \textbf{2019-2024}
		\end{minipage}
		\vspace*{0.25cm}
		\begin{minipage}{0.7\textwidth}
			PhD student at Max Planck Institute for Software Systems, Germany
			
			Supervisor: Jo\"el Ouaknine 
			
			Thesis: Algorithmic verification of linear dynamical systems.
			Received the grade \emph{summa cum laude}.
			Nominated for the Otto Hahn Medal of the Max Planck Society (outcome pending).
		\end{minipage}
		\vspace{0.25cm}
		\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{2015-2019}
		\end{minipage}
	\begin{minipage}{0.7\textwidth}
		MCompSci Computer Science, University of Oxford, UK
		
		First Class Honours
		
		Bachelor's thesis: On the Černý conjecture in theory of finite automata
		
		Master's thesis: Synchronization problems in Markov decision processes 
	\end{minipage}
	\vspace{0.25cm}
	\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{2013-2015}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		IB Diploma Programme, D\"unya School, Baku, Azerbaijan
	\end{minipage}

	\section*{Research Areas}
	\begin{itemize}
		\item Broadly speaking, I am interested in applying techniques from algebra, number theory, dynamical systems, and logic to solving open problems in theoretical computer science and control theory. 
		\item My PhD thesis is about finding algorithms that verify imperative programs (e.g. prove that a given program always terminates) using the theory of (linear) dynamical systems.
	\end{itemize}


	\section*{Publications}
	\begin{enumerate}
		\item T. Karimov
		\newline \href{https://publikationen.sulb.uni-saarland.de/handle/20.500.11880/37285}{Algorithmic verification of linear dynamical systems.}
		\newline\emph{PhD thesis, 2024, Saarland University.}
		
		\item V. Berth\'e, T. Karimov, J. Nieuwveld, J. Ouaknine, M. Vahanwala, and J. Worrell.
		\newline\href{https://doi.org/10.1145/3661814.3662119}{On the decidability of monadic second-order logic with arithmetic predicates.}
		\newline\emph{Proc. of LICS 2024.} \textbf{Distinguished Paper Award.} 
		
		\item R. Aghamov, C. Baier, T. Karimov, J. Piribauer, and J. Ouaknine.
		\newline\href{https://doi.org/10.1145/3641513.36501}{Linear dynamical systems with continuous weight functions.}
		\newline\emph{Proc. of HSCC 2024.} \textbf{ACM SIGBED Best Paper Award.}
		
		\item T. Karimov, E. Kelmendi, J. Nieuwveld, J. Ouaknine and J. Worrell.
		\newline \href{https://ieeexplore.ieee.org/document/10175758}{The Power of Positivity.}
		\newline\emph{Proc. of LICS 2023.} 
		
		\item T. Karimov, E. Kelmendi, J. Ouaknine and J. Worrell.
		\newline \href{https://doi.org/10.1007/978-3-031-22337-2_2}{What's decidable about linear dynamical systems?}
		\newline\emph{Principles of System Design--Thomas A. Henzinger Festschrift, LNCS 13660, 2022.}
		
		\item C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, J. Ouaknine, D. Purser, M. Whiteland, and J. Worrell. 
		\newline \href{https://drops.dagstuhl.de/opus/volltexte/2022/17073/}{Parameter synthesis for parametric probabilistic dynamical systems and prefix-independent specifications.}
		\newline\emph{Proc. of CONCUR 2022, LIPIcs 243.}
		
		\item J. D'Costa, T. Karimov, R. Majumdar, J. Ouaknine, M. Salamati, and J. Worrell. 
		\newline \href{https://drops.dagstuhl.de/opus/volltexte/2022/16838/}{The pseudo-reachability problem for diagonalisable linear dynamical systems.}
		\newline\emph{Proc. of MFCS 2022, LIPIcs 241.}
		
		\item T. Karimov, E. Lefaucheux, J. Ouaknine, D. Purser, J. Worrell, and M. Whiteland. 
		\newline \href{https://dl.acm.org/doi/10.1145/3498727}{What's decidable about linear loops?}
		\newline\emph{POPL 2022, Proceedings of the ACM on Programming Languages, Volume 6, issue POPL.}
		
		\item C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, F. Luca, J. Ouaknine, D. Purser, M. A. Whiteland, and J. Worrell.
		\newline \href{https://people.mpi-sws.org/~joel/publications/semialgebraic-model-checking-LDS21abs.html}{The Orbit Problem for parametric linear dynamical systems.}
		\newline \emph{Proceedings of CONCUR 2021, LIPIcs 203.}
		
		\item J. D'Costa, T. Karimov, R. Majumdar, J. Ouaknine, M. Salamati, S. Soudjani, and J. Worrell.
		\newline \href{https://people.mpi-sws.org/~joel/publications/pseudo-skolem21abs.html}{The Pseudo-Skolem Problem is decidable.}
		\newline \emph{Proceedings of MFCS 2021, LIPIcs 202.}
		
		\item S. Almagor, T. Karimov, E. Kelmendi, J. Ouaknine, and J. Worrell.
		\newline \href{https://people.mpi-sws.org/~joel/publications/omega_LRS21abs.html}{Deciding $\omega$-regular properties on linear recurrence sequences}. 
		\newline
		\emph{POPL 2021, Proceedings of the ACM on Programming Languages, Volume 5, issue POPL.}
		
		\item C. Baier, F. Funke, S. Jantsch, T. Karimov, E. Lefaucheux, J. Ouaknine,
		A. Pouly, D. Purser, and M. A. Whiteland. 
		\newline
		\href{https://people.mpi-sws.org/~joel/publications/dynamical_systems_orbit_rounding20abs.html}{Reachability in dynamical systems with rounding.} 
		\newline \emph{Proceedings of FSTTCS 2020, LIPIcs 182.}
		
		\item T. Karimov, J. Ouaknine, and J. Worrell. 
		\newline \href{https://people.mpi-sws.org/~joel/publications/LTL_discrete_LDS20abs.html}{On LTL model-checking for low-dimensional discrete
			linear dynamical systems}. \newline \emph{Proceedings of MFCS 2020, LIPIcs 170.}
	\end{enumerate}
	
	\section*{Scholarships and awards}
	\begin{enumerate}
		\item CPEC mini-project award (DFG grant 389792660 as part of TRR 248, see \href{https://www.perspicuous-computing.science/}{https://www.perspicuous-computing.science}) to travel to Oxford to work with Amaury Pouly on the reachability problem for linear time-invariant systems.
		\item Keble College Scholarship, 2016-2019. Awarded for the performance at the exams each year.
		\item The Scholarship of the Ministry of Education of Azerbaijan covering the full costs of my study at the University of Oxford, 2015-2019.
	\end{enumerate}
	
	\section*{Teaching}
	\noindent\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{Summer 2020}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		Automata and Sequences, teaching assistant 
		
		University of Saarland
	\end{minipage}
	
	\vspace{0.3cm}
	
	\noindent\begin{minipage}{0.3\textwidth}
		\hspace{0.5cm} \textbf{Winter 2022}
	\end{minipage}
	\begin{minipage}{0.7\textwidth}
		Topics in Algorithmic Dynamical Systems Theory, teaching assistant 
		
		University of Saarland
	\end{minipage}
	
	\section*{Talks and Presentations}
	\begin{enumerate}
		\item The Pseudo-Reachability Problem for diagonalisable affine dynamical systems. \emph{MFCS 2022} and \emph{RP 2022}.
		\item The Pseudo-Skolem Problem is decidable. \emph{MFCS 2021}.
		\item Invariants and impossibility: from geometric constructions to solving polynomial equations. \emph{Monsoon Math 2021}.
		\item Deciding $\omega$-regular properties on linear recurrence sequences. \emph{POPL 2021.}
		\item On verification of linear dynamical systems. \emph{Lighthning Talk at MPI-SWS, 2020.}
		\item  On LTL model-checking for low-dimensional discrete
		linear dynamical systems. \emph{MFCS 2020.}
	\end{enumerate}
\end{document}